The Mechanism of Shrimpoluminescence

### 2022-01-19 sonoluminescence/paper/bak/v6/paper.tex
sdfadsfa

We can refine eq. \ref{eq:RP_1} a little further. Since the motion in the fluid is purely radial, we expect the only relevant stresses to be normal to the bubble wall. Let's denote the radial stress in the liquid at some point $r$ by $s_r(r)=-p(r,t)+2\eta \partial_r u$. Recall, $\eta$ is the fluid viscosity from earlier. Using conservation of mass and momentum, and our expression above for the velocity, we can equate the normal stresses in the fluid to those in the bubble:
\begin{equation}
\begin{split}
    s_r(R)=-p_B-4\frac{\eta \dot{R}}{R}=-p_g+2\frac{\sigma}{R}
\end{split}
\end{equation}
where $p_g$ is the pressure in the gas and $\sigma$ is the surface tension. Solving for $p_B(t)$, we have the relation \cite{brenner2002single,prosperetti1999old,prosperetti1986bubble}
\begin{equation}
    p_B(t)=p_g(t)-\frac{1}{R}\left( 2\sigma+4\eta \dot{R} \right)
    \label{eq:p_B}.
\end{equation}
Note that in deriving the equations \ref{eq:NS_1D} we neglected the viscosity terms. This was valid since only combinations of viscosity and compressibility $\nabla \cdot \bm{u}$ appeared, both of which are assumed small. Here, however, we keep the viscosity terms coupling the bubble wall to the fluid. The RP equation becomes 
\begin{equation}
    R\ddot{R}+\frac{3}{2}\dot{R}^2 = \frac{1}{\rho} \left[ \Delta p(t)-\frac{1}{R}\left( 2\sigma+4\eta \dot{R} \right)-P(t) \right]
    \label{eq:RP_2}
\end{equation}
with $\Delta p = p_g(t)-p_\infty$ the deviation of the pressure inside the bubble from the static pressure. With the above assumption that the compression is adiabatic, the conditions inside the bubble are decoupled from the liquid (besides the coupling through the RP equation) and we may regard $p_g(t)$ in the bubble as a given quantity to be determined from an equation of state. Recall $P(t)$ is the time-dependent part of the pressure in the absence of the bubble: we may regard this as an external pressure from e.g. a driving stress. In SBSL, this is from the transducers driving the flask and $P(t)$ is an acoustic plane wave. Keller and coworkers showed that the modification required to the RP equation is the replacement $P(t) \rightarrow P_0 \sin(\omega t)$ \cite{keller1980bubble}. If we linearize in the bubble's radius $R(t)\approx R_0 \left( 1+x(t) \right)$ with $x(t) \ll 1$, we can derive a forced harmonic oscillator equation for $x(t)$ \cite{brennen2014cavitation,yasui2018acoustic}. However, the low driving amplitude regime where this method is valid is irrelevant to SBSL so we won't pursue it here.

@@

The RP equation (eq. \ref{eq:RP_2}) is pretty but its analytical solution is intractable. Direct solutions of the RP equation or its variants are done numerically using e.g. Euler or Runge-Kutta methods \cite{yasui2018acoustic,yasui2015dynamics}. It is no great challenge computationally. For now, let's see what we else we can understand from this analytically by making some more approximations. If we look at the interval where the bubble wall's velocity is very large, called \emph{The Rayleigh Collapse}, the right hand side of eq. \ref{eq:RP_2} will be much smaller than the $\dot{R}^2$ term and we may neglect it \cite{rayleigh1917pressure,plesset1949dynamics,prosperetti1999old,brenner2002single}. 
Rayleigh looked at the same problem, i.e. a cavitating void in water:
\begin{equation}
    R\ddot{R}+\frac{3}{2}\dot{R}^2=0
    \label{eq:Rayleigh}
\end{equation}
and found the solution to be $R(t)\sim\left(t_*-t\right)^{2/5}$ \cite{brenner2002single}, with $t_*$ the time of collapse. The velocity, $\dot{R}\sim\left(t_*-t \right)^{-3/5}$, diverges as the bubble collapses. This observation is what lead to Rayleigh's argument for the origin of cavitation damage to ship's propellers. %Yasui gave a rather elegant heuristic explanation for the origin of \emph{cavitation} in a fluid that is worth stating here \cite{yasui2018acoustic}. Consider the mass flowing through concentric shells around a bubble, $4\pi R_i^2 v_i \rho$. For a source free field, we require that neighboring shells satisfy conservation of mass: $4\pi R_1^2 v_1 = 4\pi R_2^2 v_2$. For $R_2 > R_1$, we see that $v_1/v_2 = \left(R_2/R_1\right)^2$. The velocity for a smaller radius is always larger, diverging towards the origin.

@@

@@

Some attempts were made to measure SBSL using non-aqueous host liquids e.g. alcohols, silicone oils \cite{weninger1995sonoluminescence,barber1997defining}, but experiments with air bubbles were not very successful \cite{barber1997defining}. Eventually, different gases were tried in water. Recall, air is $\sim 80\%$ N$_2$, $\sim 20\%$ O$_2$, and $\sim 1\% $ Ar. Considering the relatively large content of O$_2$ and N$_2$, degassed water \emph{regassed} with N$_2$ or O$_2$ or a mixture were checked first and found not to produce SBSL \cite{hiller1994effect}. What was discovered was that a small amount of noble gas was required for SBSL to occur \cite{barber1997defining,hiller1994effect,brenner2002single}. A result of this work was the \emph{argon rectification hypothesis} \cite{lohse1997sonoluminescing,brenner2002single,yasui2018acoustic,suslick2008inside}. The hypothesis claims that all species in the air inside the bubble besides argon are gradually ejected from bubble's interior until all that remains is pure argon. The theory is based on the fact that, at the elevated temperatures and pressures inside the bubble, dissociation of O$_2$ and N$_2$ into radicals is possible. These species then react with the water vapor radicals to form species that are soluble in the host fluid. As the pressure becomes very large during the compression stage of SBSL, the soluble materials leave the bubble and do not re-enter since their solubility in water is enormous compared to the Ar content of the bubble \cite{lohse1997sonoluminescing}. Over many cycles, the contents of an air bubble in water become nearly pure argon. Moreover, it was hypothesized that the SL would much more intense when the contents of the bubble are a pure inert gas: if the contents were e.g. molecules, bond breaking/formation would alter the pressure of the gas, ultimately reducing the temperature and reducing the amount of light production \cite{brenner2002single,yasui2018acoustic,lohse2018bubble,suslick2008inside}. This mechanism has been used to explain the relatively weak light, i.e. the low temperature, in MBSL: the bubbles are transient and cannot remove a significant amount of O$_2$ or N$_2$ over a single cycle. The current belief is that the contents of a bubble undergoing SBSL in water are pure argon after $\sim 10^3$ cycles \cite{brenner2002single,yasui2018acoustic}.

Still, most studies continued to use water as the host liquid until it was realized that SBSL in aqueous H$_2$SO$_4$ produces light $10^3$ times brighter than in water, allowing more precise measurements of the light spectrum \cite{}. More importantly, new measurements revealed the phase space of SBSL in aqueous H$_2$SO$_4$ included a much larger range of pressure than water. Careful experiments revealed that the spectrum depended critically on the noble gas content and driving pressure. Suslick et. al measured the different emission spectra from Ar, Xe, and Kr bubbles in aqueous H$_2$SO$_4$, driven to have similar conditions to those in an air bubble in water \cite{flannigan2005plasma,flannigan2006measurement,suslick2008inside}. Importantly, they were able to identify spectral lines from Ar$^+$, Xe$^+$, and Kr$^+$ excited state transitions, proving that the core of the bubble is plasma. Perhaps equally as crucially, they found the absence of emission lines from components of aqueous H$_2$SO$_4$ vapor \cite{suslick2008inside,flannigan2006measurement,flannigan2006measurement}: the plasma contained only the noble gas, experimentally confirming the argon rectification hypothesis. Moreover, the spectra at different pressures were in very good agreement with detailed calculations of emission from noble gas plasmas \cite{an2009diagnosing,an2008spectral}. Increased pressure results in increased collision rate between particles, broadening the excited state transition spectral lines \cite{an2008spectral,suslick2008inside,flannigan2005plasma,flannigan2006measurement}. Further calculations showed that the greatly increased viscosity and density of aqueous H$_2$SO$_4$, $\sim 10 \times$ and $\sim 1.3 \times$ larger than that that of water, lead to reduced (by orders of magnitude) pressure in the bubble at the same driving pressures \cite{an2009diagnosing}. The larger pressure in the bubbles in water was found to be consistent with the featureless emission spectrum \cite{suslick2008inside,yasui2018acoustic}.

This argon rectification hypothesis greatly helped to refine models for the gas dynamics in the bubble and clarified several unexplained experimental observations \cite{suslick2008inside,brenner2002single}. With this in mind, we choose only to focus on results known to be relevant to the dynamics of a bubble undergoing SBSL. Excellent books and modern reviews on modeling the gas dynamics exist elsewhere \cite{brenner2002single,yasui2018acoustic,brennen2014cavitation}. We will hold off on discussing the dynamics in the plasma until a later section.

\subsection{Gas Dynamics}
The most straightforward way to model the gas dynamics in the bubble is through direct solution of the Navier-Stokes equations for the gas \cite{brenner2002single}. In fact, serious quantitative predictions of the conditions of the bubble's interior take this path \cite{an2006mechanism,an2008spectral,an2009diagnosing,flannigan2005plasma,flannigan2006measurement}. With simplifying assumptions, equations of motion with varying degrees of sophistication can be derived for the gas and the system of gas dynamical equations and the RP equations are solved numerically. The discussion proceeds in much the same way as deriving the RP equations above but is considerably more complicated \cite{brenner2002single,yasui2018acoustic}, so we will omit it here. An important aspect of these studies is the understanding of why relatively simple models work quite well. We will highlight the salient features before introducing a simple model for the gas that will enable us to gain some physical understanding analytically. An especially important result of direct numerical solution of the gas dynamics was (theoretical) confirmation of the argon rectification hypothesis \cite{}, reducing the possible gas dynamical models to those applicable to a monatomic gas. Various other models fully including dissipation and heat transport into/out of the bubble showed that the bubble's compression is, to a good approximation, adiabatic and quasistatic \cite{}. Before we turn to discuss a model for the gas dynamics, let us pause to mention that another theoretically appealing method for modeling the gas dynamics is \emph{molecular dynamics} \cite{}. While this method is attractive for a number of reasons, practical calculations containing realistic numbers of particles aren't possible, limiting the applicability \cite{brenner2002single}.

A simple but reasonable model for the gas dynamics in the bubble is that of an adiabatically, quasistatically compressed ideal gas \cite{brenner2002single} \footnote{Actually we want to study a \emph{Van der Walls} gas, but we will sneak this aspect in later. The modifications to the result for an ideal gas are simple \cite{sivasubramanian2002temperature}.}. Let us remind ourselves what the pressure is in this case. Suppose that we have a volume, $V$, of an ideal gas containing $N$ particles at a temperature $T$. The ideal gas law tells us the equation of state is $PV=Nk_BT$ with $k_B$ Boltzmann's constant. Since we are assuming adiabatic compression, the second law of thermodynamics tells us that $dU=-PdV$ with $U$ the internal energy in the gas. Moreover, we may use the equipartition theorem to write $dU=N f k_B dT/2$ with $f$ the number of degrees-of-freedom per particle \cite{schroeder1999introduction}. Recall that for an ideal gas $C_V = N f k_B/2$, $C_P = C_V+N k_B$, and $C_P/C_V = 1+2/f \equiv \gamma$ with $C_V$ and $C_P$ the heat capacities at constant volume and pressure respectively. For a monatomic ideal gas, $f=3$ and $\gamma=5/3$. Now we can use the second law of thermodynamics to write $C_V dT = -P dV$. From the equation of state, we have
\begin{equation}
    dT = \frac{PdV+VdP}{Nk_B}=\frac{PdV+VdP}{C_P-C_V}.
\end{equation}
Eliminating $dT$ and simplifying, 
\begin{equation}
    \frac{dP}{P}=-\left(\frac{C_P}{C_V}\right) \frac{dV}{V} = -\gamma \frac{dV}{V}.
    \label{eq:dP}
\end{equation}
Integrating eq. \ref{eq:dP}, we find 
\begin{equation}
    P_2 = P_1 \left(\frac{V_1}{V_2}\right)^\gamma
\label{eq:P}
\end{equation}
where $P_2$ is the pressure in a gas at volume $V_2$ that was initially contained in a volume $V_1$ at pressure $P_1$. Importantly we have not made any assumptions about the shape of the container.

@@

Our physical intuition tells us why eq. \ref{eq:p_g} is sensible during the bubble's collapse: the bubble wall's velocity is fast and very little heat can flow out during compression. Detailed calculations starting from the full NS equations further tell us that the gas dynamics in the bubble can be regarded as \emph{quasistatic} \cite{}. During the expansion and after-bounce stages of the bubbles cycle, which comprise its majority, the gas dynamics should instead be regarded as \emph{isothermal}. This is true because, when the bubble's velocity is on the order of the heat diffusion timescale, the temperature throughout the bubble is nearly equal to that in the liquid \cite{prosperetti1999old,brenner2002single,yasui2018acoustic}. The relevant modifications to eq. \ref{eq:p_g} turns out to be replacing $\gamma\rightarrow 1$. A neat way of including both isothermal and adiabatic gas dynamics is continuously varying the exponent, $\gamma$ in eq. \ref{eq:p_g}, between its adiabatic and isothermal values, $C_P/C_V$ and $1$, respectively. A summary of this work is given in refs. \cite{brenner2002single} and \cite{prosperetti1999old}. It turns out that this process doesn't result in better quantitative predictions since, during the assumed isothermal part of the process, dissipation becomes important \cite{brenner2002single}. A simple alternative is choosing a constant exponent somewhere between the adiabatic $\gamma=5/3$ and isothermal $\gamma=1$ values \cite{hilgenfeldt1999simple}. It is also possible to include heat and mass diffusion in simple model forms and these do give slightly improved quantitative agreement with experiment; however we choose to discuss solutions of the RP equations using the simpler form given in eq. \ref{eq:p_g} as this will enable to understand the important features of the bubble's cycle. More advanced solutions using the full gas dynamical equations are qualitatively similar \cite{brenner2002single,yasui2018acoustic}.

Now recall that one of main goals of modeling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ {\gamma-1}.
    \label{eq:T(t)}
\end{equation}
Earlier, we assumed that during the bubble's after-bounces and expansion, the gas dynamics were isothermal. Then we take $T_0$ to be the temperature of the liquid. The RP equation, eq. \ref{eq:RP_3}, combined with the gas dynamical equation, eq. \ref{eq:p_g}, and the known liquid and gas properties $\eta$, $\sigma$, and $h$, can be used to calculate the dynamics of an acoustically driven bubble, determining the time-dependence of the pressure and temperature in the bubble along the way.

\subsection{Bubbles in the Lab}
\begin{figure}
\includegraphics[width=0.9\linewidth]{figs/bubble_radius_1.pdf}
    \caption{\cite{barber1997defining,barber1992light}}
\label{fig:bubble_radius_1}
\end{figure}

Creating stable, single bubbles in a laboratory experiment is not particularly challenging and can be done with standard and low-cost materials \footnote{Actually, the phase-space for SBSL is ``small". The coordinates being driving amplitude, driving frequency, fluid composition, temperature, ambient pressure, gas content and composition, etc... What we are claiming is simple is the experimental setup once the correct parameters are identified.}. A typical experimental setup is shown in Fig. \ref{fig:flask}. Since we are mainly concerned with the explaining the light emission process itself, we will only sketch the experimental setup; it can be summarized as follows \cite{lentz1995mie,gaitan1990experimental,gaitan1992sonoluminescence,gompf2000mie,brenner2002single,yasui2018acoustic,brennen2014cavitation,suslick2008inside}. A sample of degassed liquid is placed into a flask \footnote{Actually, the degassing part is quite important. We focus on it elsewhere.}. Coupled to the outside of the flask are piezoelectric transducers of some sort. The piezos are driven by a sinusoidal function generator to excite an acoustic resonance of the flask: a typical flask is a few cm across with a resonance at $\approx 20$ kHz \cite{brenner2002single}. The frequency is chosen to form a pressure \emph{antinode} at the center of the flask.

Let us take a brief aside: in deriving the RP equations, we assumed the center of the bubble was stationary. Actually, this is what we want in an SBSL experiment and it is worth discussing under what conditions this is true. In an ideal, incompressible fluid the net force acting on a bubble may be written as 
\begin{equation}
    \bm{f}=-\int_{\partial \Omega} p \bm{n} dA = -\int_\Omega \nabla p dV
\end{equation}
Here, $\bm{f}$ is the net force, $p$ is the pressure at the bubble's surface, $\bm{n}$ is the unit normal vector point out of the bubbles surface, and $\partial \Omega$ is the bubble's boundary with $\Omega$ the bubble's domain. The last term is due to an application of Gauss's theorem. Bjerknes \cite{bjerknes1909kraftfelder} took $\nabla p \equiv \nabla p(r=0,t)$ to be constant and averaged over one period of oscillation to find 
\begin{equation}
    \bm{f} = -\frac{4}{3}\pi \langle R^3 \nabla p \rangle.
    \label{eq:Bj_force}
\end{equation}
This is the so called \emph{Bjerknes force}. The point is that if the bubble is located at a pressure extrema, e.g. the antinode at the center of the flask, then this force should vanish and the bubble will remain stationary, an essential result for SBSL experiments.

>>>>

We can refine eq. \ref{eq:RP_1} a little further. Since the motion in the fluid is purely radial, we expect the only relevant stresses to be normal to the bubble wall. Let's denote the radial stress in the liquid at some point $r$ by $s_r(r)=-p(r,t)+2\eta \partial_r u$. Recall, $\eta$ is the fluid viscosity from earlier. Using conservation of mass and momentum, and our expression above for the velocity, we can equate the normal stresses in the fluid to those in the bubble:
\begin{equation}
\begin{split}
    s_r(R)=-p_B-4\frac{\eta \dot{R}}{R}=-p_g+2\frac{\sigma}{R}
\end{split}
\end{equation}
where $p_g$ is the pressure in the gas and $\sigma$ is the surface tension. Solving for $p_B(t)$, we have the relation \cite{brenner2002single,prosperetti1999old,prosperetti1986bubble}
\begin{equation}
    p_B(t)=p_g(t)-\frac{1}{R}\left( 2\sigma+4\eta \dot{R} \right)
    \label{eq:p_B}.
\end{equation}
Note that in deriving the equations \ref{eq:NS_1D} we neglected the viscosity terms. This was valid since only combinations of viscosity and compressibility $\nabla \cdot \bm{u}$ appeared, both of which are assumed small. Here, however, we keep the viscosity terms coupling the bubble wall to the fluid. The RP equation becomes 
\begin{equation}
    R\ddot{R}+\frac{3}{2}\dot{R}^2 = \frac{1}{\rho} \left[ \Delta p(t)-\frac{1}{R}\left( 2\sigma+4\eta \dot{R} \right)-P(t) \right]
    \label{eq:RP_2}
\end{equation}
with $\Delta p = p_g(t)-p_\infty$ the deviation of the pressure inside the bubble from the static pressure. With the above assumption that the compression is adiabatic, the conditions inside the bubble are decoupled from the liquid (besides the coupling through the RP equation) and we may regard $p_g(t)$ in the bubble as a given quantity to be determined from an equation of state. Recall $P(t)$ is the time-dependent part of the pressure in the absence of the bubble: we may regard this as an external pressure from e.g. a driving stress. In SBSL, this is from the transducers driving the flask and $P(t)$ is an acoustic plane wave. Keller and coworkers showed that the modification required to the RP equation is the replacement $P(t) \rightarrow P_0 \sin(\omega t)$ \cite{keller1980bubble}.

@@

The RP equation (eq. \ref{eq:RP_2}) is pretty but its analytical solution is intractable. Direct solutions of the RP equation or its variants are done numerically using e.g. Euler or Runge-Kutta methods \cite{yasui2018acoustic,yasui2015dynamics}. It is no great challenge computationally. For now, let's see what we can understand analytically by making some more approximations. If we linearize in the bubble's radius $R(t)\approx R_0 \left( 1+x(t) \right)$ with $x(t) \ll 1$, we can derive a forced harmonic oscillator equation for $x(t)$ \cite{brennen2014cavitation,yasui2018acoustic}. However, the low driving amplitude regime where this method is valid is irrelevant to SBSL so we won't pursue it here. Instead, we can look at the interval where the bubble wall's velocity is very large, called \emph{The Rayleigh Collapse}; the right hand side of eq. \ref{eq:RP_2} will be much smaller than the $\dot{R}^2$ term and we may neglect it \cite{rayleigh1917pressure,plesset1949dynamics,prosperetti1999old,brenner2002single}. 
Rayleigh looked at the same problem, i.e. a cavitating void in water:
\begin{equation}
    R\ddot{R}+\frac{3}{2}\dot{R}^2=0
    \label{eq:Rayleigh}
\end{equation}
and found the solution to be $R(t)\sim\left(t_*-t\right)^{2/5}$ \cite{brenner2002single}, with $t_*$ the time of collapse. The velocity, $\dot{R}\sim\left(t_*-t \right)^{-3/5}$, diverges as the bubble collapses. This observation is what lead to Rayleigh's argument for the origin of cavitation damage to ship's propellers. %Yasui gave a rather elegant heuristic explanation for the origin of \emph{cavitation} in a fluid that is worth stating here \cite{yasui2018acoustic}. Consider the mass flowing through concentric shells around a bubble, $4\pi R_i^2 v_i \rho$. For a source free field, we require that neighboring shells satisfy conservation of mass: $4\pi R_1^2 v_1 = 4\pi R_2^2 v_2$. For $R_2 > R_1$, we see that $v_1/v_2 = \left(R_2/R_1\right)^2$. The velocity for a smaller radius is always larger, diverging towards the origin.

@@

Above, we assumed that the bubble always remains spherical. Of course this isn't always true and \emph{shape-instabilities} occur for the right combinations of mechanical properties and driving force/frequency. Usually shape-instabilities destroy the bubble and kill SBSL so we won't focus on these isues here. We will always assume we are in a parameter-regime where SBSL occurs. The reader is referred to one of several reviews on the \emph{phase-space} of SBSL for more info \cite{yasui2018acoustic,brenner2002single,hilgenfeldt1999sonoluminescence,an2009diagnosing}.

@@

Some attempts were made to measure SBSL using non-aqueous host liquids e.g. alcohols, silicone oils \cite{weninger1995sonoluminescence,barber1997defining}, but experiments with air bubbles were not very successful \cite{barber1997defining}. Eventually, different gases were tried in water. Recall, air is $\sim 80\%$ N$_2$, $\sim 20\%$ O$_2$, and $\sim 1\% $ Ar. Considering the relatively large content of O$_2$ and N$_2$, degassed water \emph{regassed} with N$_2$ or O$_2$ or a mixture were checked first and found not to produce SBSL \cite{hiller1994effect}. What was discovered was that a small amount of noble-gas was required for SBSL to occur \cite{barber1997defining,hiller1994effect,brenner2002single}. A result of this work was the \emph{argon rectification hypothesis} \cite{lohse1997sonoluminescing,brenner2002single,yasui2018acoustic,suslick2008inside}. The hypothesis claims that all species in the air inside the bubble besides argon are gradually ejected from bubble's interior until all that remains is pure argon. The theory is based on the fact that, at the elevated temperatures and pressures inside the bubble, dissociation of O$_2$ and N$_2$ into radicals is possible. These species then react with the water vapor radicals to form species that are soluble in the host fluid. As the pressure becomes very large during the compression stage of SBSL, the soluble materials leave the bubble and do not re-enter since their solubility in water is enormous compared to the Ar content of the bubble \cite{lohse1997sonoluminescing}. Over many cycles, the contents of an air bubble in water become nearly pure argon. Moreover, it was hypothesized that the SL would be much more intense when the contents of the bubble are a pure inert gas: if the contents were e.g. molecules, bond breaking/formation would alter the pressure of the gas, ultimately reducing the temperature and reducing the amount of light production \cite{brenner2002single,yasui2018acoustic,lohse2018bubble,suslick2008inside}. This mechanism has been used to explain the relatively weak light, i.e. the low temperature, in MBSL: the bubbles are transient and cannot remove a significant amount of O$_2$ or N$_2$ over a single cycle. The current belief is that the contents of a bubble undergoing SBSL in water are (nearly) pure argon after $\sim 10^3$ cycles \cite{brenner2002single,yasui2018acoustic}.

Still, most studies continued to use water as the host liquid until it was realized that SBSL in aqueous H$_2$SO$_4$ produces light $10^3$ times brighter than in water, allowing more precise measurements of the light spectrum \cite{flannigan2005plasma,flannigan2006measurement}. The mechanical properties in aqueous H$_2$SO$_4$ allow stable SBSL with a larger bubble radii than in water, increasing the emitting volume. More importantly, new measurements revealed the phase space of SBSL in aqueous H$_2$SO$_4$ included a much larger range of pressure than water. SBSL in aqueous H$_2$SO$_4$ could be driven at very low pressure, leading to much lower temperature bubbles, while driving at large pressure led to conditions similar to SBSL in water.

Careful experiments revealed that the spectrum depended critically on the noble-gas content and driving pressure. Suslick et. al measured the different emission spectra from Ar, Xe, and Kr bubbles in aqueous H$_2$SO$_4$, driven to have similar conditions to those in an air bubble in water \cite{flannigan2005plasma,flannigan2006measurement,suslick2008inside}. Importantly, they were able to identify spectral lines from Ar$^+$, Xe$^+$, and Kr$^+$ excited state transitions, proving that the core of the bubble is plasma. Perhaps equally as crucially, they found the absence of emission lines from components of aqueous H$_2$SO$_4$ vapor \cite{suslick2008inside,flannigan2006measurement,flannigan2006measurement}: the plasma contained only the noble-gas, experimentally confirming the argon rectification hypothesis. The spectra at different pressures were in very good agreement with detailed calculations of emission from noble-gas plasmas \cite{an2009diagnosing,an2008spectral}. This work also explained why the spectrum in water is featureless (i.e. has no emission lines). The larger pressure in SBSL in water results in an increased collision rate between particles, broadening the spectral lines \cite{an2009diagnosing,suslick2008inside,flannigan2005plasma,flannigan2006measurement}.

This argon rectification hypothesis greatly helped to refine models for the gas dynamics in the bubbles and confirmed why simple models usually work well \cite{suslick2008inside,brenner2002single}. With this in mind, we choose only to focus on results known to be relevant to the dynamics of a bubble undergoing SBSL. Excellent books and modern reviews on modeling the gas dynamics exist elsewhere \cite{brenner2002single,yasui2018acoustic,brennen2014cavitation}. We will hold off on discussing the plasma until a later section.

\subsection{Gas Dynamics}
Of course the most straightforward way to model the gas dynamics in the bubble is through direct solution of the Navier-Stokes equations for the gas \cite{brenner2002single}. In fact, serious quantitative predictions of the conditions of the bubble's interior still take this path \cite{an2006mechanism,an2008spectral,an2009diagnosing,flannigan2005plasma,flannigan2006measurement}. With simplifying assumptions, equations of motion with varying degrees of sophistication can be derived for the gas and the system of gas dynamical equations and the RP equations are solved numerically. The discussion proceeds in much the same way as deriving the RP equations above but is slighlty more complicated \cite{brenner2002single,yasui2018acoustic}, so we will omit it. An important aspect of these studies is the understanding of why relatively simple models work quite well.

We will highlight the salient features before introducing a simple model for the gas that will enable us to gain some physical understanding analytically. An especially important result of direct numerical solution of the gas dynamics was (theoretical) confirmation of the argon rectification hypothesis, reducing the possible gas dynamical models to those applicable to a monatomic gas. Various other models fully including dissipation and heat transport into/out of the bubble showed that the bubble's compression is, to a good approximation, adiabatic and quasistatic. Before we turn to discuss a model for the gas dynamics, let us pause to mention that another theoretically appealing method for modeling the gas dynamics is \emph{molecular dynamics}. While this method is attractive for a number of reasons, practical calculations containing realistic numbers of particles aren't possible, limiting the applicability \cite{brenner2002single}.

Recalling that the bubble is (almost) purely noble-gas, a simple but reasonable model for the gas dynamics is that of an adiabatically, quasistatically compressed ideal\footnote{Actually a \emph{Van der Walls} gas model is better, but we will sneak this aspect in later. The modifications to the result for an ideal gas are simple \cite{sivasubramanian2002temperature}.} gas \cite{brenner2002single}. Let us remind ourselves what the pressure is. Suppose that we have a volume, $V$, of an ideal gas containing $N$ particles at a temperature $T$. The ideal gas law tells us the equation of state is $PV=Nk_BT$ with $k_B$ Boltzmann's constant. Since we are assuming adiabatic compression, the second law of thermodynamics is $dU=-PdV$ with $U$ the internal energy in the gas. We may use the equipartition theorem to write $dU=N f k_B dT/2$ with $f$ the number of degrees-of-freedom per particle \cite{schroeder1999introduction}. Recall that for an ideal gas the specific heat at constant volume is $C_V = N f k_B/2$ and at constant pressure is $C_P = C_V+N k_B$, with $C_P/C_V = 1+2/f \equiv \gamma$. For a noble-gas, $f=3$ and $\gamma=5/3$. Now we can use the second law of thermodynamics to write $C_V dT = -P dV$. From the equation of state, we have
\begin{equation}
    dT = \frac{PdV+VdP}{Nk_B}=\frac{PdV+VdP}{C_P-C_V}.
\end{equation}
Inserting $dT$ into the second law and simplifying, 
\begin{equation}
    \frac{dP}{P}=-\left(\frac{C_P}{C_V}\right) \frac{dV}{V} = -\gamma \frac{dV}{V}.
    \label{eq:dP}
\end{equation}
Integrating eq. \ref{eq:dP}, we find 
\begin{equation}
    P_2 = P_1 \left(\frac{V_1}{V_2}\right)^\gamma
\label{eq:P}
\end{equation}
where $P_2$ is the pressure in a gas at volume $V_2$ that was initially contained in a volume $V_1$ at pressure $P_1$. Importantly we have not made any assumptions about the shape of the container.

@@

Our physical intuition tells us why eq. \ref{eq:p_g} is sensible during the bubble's collapse: the bubble wall's velocity is fast and very little heat can flow out during compression. Detailed calculations starting from the full NS equations further tell us that the gas dynamics in the bubble can be regarded as \emph{quasistatic} \cite{brenner2002single}. During the expansion and after-bounce stages of the bubbles cycle, which comprise its majority, the gas dynamics should instead be regarded as \emph{isothermal}. This is true because, when the bubble's velocity is on the order of the heat diffusion timescale, the temperature throughout the bubble is nearly equal to that in the liquid \cite{prosperetti1999old,brenner2002single,yasui2018acoustic}. The relevant modifications to eq. \ref{eq:p_g} turns out to be replacing $\gamma\rightarrow 1$. A neat way of including both isothermal and adiabatic gas dynamics is continuously varying the exponent, $\gamma$ in eq. \ref{eq:p_g}, between its adiabatic and isothermal values, $C_P/C_V$ and $1$, respectively. A summary of this work is given in refs. \cite{brenner2002single} and \cite{prosperetti1999old}. It turns out that this process doesn't result in better quantitative predictions since, during the assumed isothermal part of the process, dissipation becomes important \cite{brenner2002single}. A simple alternative is choosing a constant exponent somewhere between the adiabatic $\gamma=5/3$ and isothermal $\gamma=1$ values \cite{hilgenfeldt1999simple}. It is also possible to include heat and mass diffusion in simple model forms and these do give slightly improved quantitative agreement with experiment; however the simpler form given in eq. \ref{eq:p_g} gives close to the correct dynamics (see fig. \ref{fig:bubble_radius_1}). More advanced solutions using the full gas dynamical equations are qualitatively similar \cite{brenner2002single,yasui2018acoustic}.

Now recall that one of main goals of modeling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ {\gamma-1}.
    \label{eq:T(t)}
\end{equation}
Earlier, we said that during the bubble's after-bounces and expansion, the gas dynamics is isothermal; then we take $T_0$ to be the temperature of the liquid. The RP equation, eq. \ref{eq:RP_3}, combined with the gas dynamical equation, eq. \ref{eq:p_g}, and the known liquid and gas properties $\eta$, $\sigma$, and $h$, can be used to calculate the dynamics of an acoustically driven bubble, giving us the time-dependence of the pressure and temperature in the bubble.

\subsection{Bubbles in the Lab}
\begin{figure}
\includegraphics[width=0.9\linewidth]{figs/bubble_radius_1.pdf}
    \caption{Numerical solution of the RP equation variant eq. \ref{eq:RP_3} with the gas dynamics given by eq. \ref{eq:p_g} compared to Mie scattering results \cite{barber1997defining,barber1992light}.}
\label{fig:bubble_radius_1}
\end{figure}

Creating stable, single bubbles in a laboratory experiment is not particularly challenging and can be done with standard and low-cost materials \footnote{Actually, the phase-space for SBSL is ``small". The coordinates being driving amplitude, driving frequency, fluid composition, temperature, ambient pressure, gas content and composition, etc... What we are claiming is simple is the experimental setup once the correct parameters are identified.}. A typical experimental setup is shown in fig. \ref{fig:flask}. Since we are mainly concerned with the explaining the light emission process itself, we will only sketch the experimental setup; it can be summarized as follows \cite{lentz1995mie,gaitan1990experimental,gaitan1992sonoluminescence,gompf2000mie,brenner2002single,yasui2018acoustic,brennen2014cavitation,suslick2008inside}. A suitable sample of liquid is placed into a flask. Coupled to the outside of the flask are piezoelectric transducers of some sort. The piezos are driven by a sinusoidal function generator to excite an acoustic resonance of the flask: a typical flask is a few cm across with a resonance at $\approx 20$ kHz \cite{brenner2002single}. The frequency is chosen to form a pressure \emph{antinode} at the center of the flask.

%Let us take a brief aside: in deriving the RP equations, we assumed the center of the bubble was stationary. Actually, this is what we want in an SBSL experiment and it is worth discussing under what conditions this is true. In an ideal, incompressible fluid the net force acting on a bubble may be written as 
%\begin{equation}
%    \bm{f}=-\int_{\partial \Omega} p \bm{n} dA = -\int_\Omega \nabla p dV
%\end{equation}
%Here, $\bm{f}$ is the net force, $p$ is the pressure at the bubble's surface, $\bm{n}$ is the unit normal vector point out of the bubbles surface, and $\partial \Omega$ is the bubble's boundary with $\Omega$ the bubble's domain. The last term is due to an application of Gauss's theorem. Bjerknes \cite{bjerknes1909kraftfelder} took $\nabla p \equiv \nabla p(r=0,t)$ to be constant and averaged over one period of oscillation to find 
%\begin{equation}
%    \bm{f} = -\frac{4}{3}\pi \langle R^3 \nabla p \rangle.
%    \label{eq:Bj_force}
%\end{equation}
%This is the so called \emph{Bjerknes force}. The point is that if the bubble is located at a pressure extrema, e.g. the antinode at the center of the flask, then this force should vanish and the bubble will remain stationary, an essential result for SBSL experiments.

%Some authors have looked at corrections to the bubble's dynamics in the presence of buoyancy, which cause translational motion even for vanishing Bjerknes force. The result is the bubble oscillates around an equilibrium position near but away from the center of the flask \cite{matula2000single,matula1997bjerknes,matula1999inertial}. The translational motion of the bubble leads to shape distortion which is believed to suppress SL; this is confirmed by SBSL experiments in microgravity resulting in larger intensity light production \cite{matula2000single}.
